### 2020-01-22 experiments.tex
RQs
more on RQ1

\section{Comparison and Improvements of Static Analysis Tools}

>>>>

\section{Experimental Results: Comparison and Improvement of Static Analysis Tools}

For each language, RQs:

RQ1:  actionable, novel differences for tool ranking?  in particular, does the rate of mutant detection differ from what would be expected by extrapolating from issue counts over original code; that is, is the tendency of mutants to represent faults/bad code useful, and avoids the problem of simply rewarding false positive-prone tools?
RQ2:  tool overlaps identifiable?
RQ3:  agrees with other sources of information?
RQ4:  can identify improvements?
